Operational Feature Selection with Gaussian Mixture Models for remote sensing images

### 2016-10-14 paper.tex
change url

    The proposed  method has been implemented  in \texttt{C++} through
    the  Orfeo  Toolbox (OTB)~\cite{christophe2008orfeo}.   The  Orfeo
    Toolbox  is  an  open-source  library  for  remote  sensing  image
    processing,  developed by  the  French Space  Agency (CNES).   The
    feature selection algorithm  can be installed as  a remote module,
    the           source            code           is           freely
    available\footnote{\url{https://github.com/Laadr/otbFFSforGMM}}.

@@

The resulting code is available as a remote module of the Orfeo toolbox on Github and makes it possible to process large high dimensional images efficiently. The \texttt{C++} code is freely available for download: \url{https://github.com/Laadr/otbFFSforGMM}.

@@

% The python and C++ code are available freely for download: \url{https://github.com/Laadr/FFFS}, .

>>>>

    The proposed  method has been implemented  in \texttt{C++} through
    the  Orfeo  Toolbox (OTB)~\cite{christophe2008orfeo}.   The  Orfeo
    Toolbox  is  an  open-source  library  for  remote  sensing  image
    processing,  developed by  the  French Space  Agency (CNES).   The
    feature selection algorithm  can be installed as  a remote module,
    the           source            code           is           freely
    available\footnote{\url{https://www.orfeo-toolbox.org/external-projects/}}.

@@

The resulting code is available as a remote module of the Orfeo toolbox on Github and makes it possible to process large high dimensional images efficiently. The \texttt{C++} code is freely available for download: \url{https://www.orfeo-toolbox.org/external-projects/}.

@@

% The python and C++ code are available freely for download: \url{https://www.orfeo-toolbox.org/external-projects/}, .
